---
title: "Age"
author: "Ink"
date: "April 14, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Cleaning up data (Given by Sanjeev)
```{r}
speed <- read.csv("Speed Dating Data.csv")
speed$condtn <- as.factor(speed$condtn)
speed$gender <- as.factor(speed$gender)
speed$match <- as.factor(speed$match)
speed$field_cd <- as.factor(speed$field_cd)
levels(speed$field_cd) <- c("Law","Math","SocScie/Psych", "MedSci", "Engineering", "English", "History", "Business", "Education", "Bio","SocialWork","Undergrad", "PoliSci", "Film","FineArts","Lang","Architecture","Other")
speed$race <- as.factor(speed$race)
speed$goal <- as.factor(speed$goal)
levels(speed$goal) <- c("FunNightOut", "MeetNewPpl", "GetADate","SRSRelationship", "ToSayIDidIt","Other")
speed$date <- as.factor(speed$date)
levels(speed$date) <- c("SVRL/Week","2/Week","1/Week","2/Month", "1/Month", "SVRL/Year", "AlmostNever")
speed$go_out <- as.factor(speed$go_out)
levels(speed$go_out) <- c("SVRL/Week","2/Week","1/Week","2/Month", "1/Month", "SVRL/Year", "AlmostNever")
speed$career_c <-as.factor(speed$career_c)
levels(speed$career_c) <- c("Lawyer","Academic/Research","Psychologist","DocMed", "Engineer", "Entertainment", "Banking/Consulting", "RealEstate","IntlAffairs","Undecided","SocialWork","SpeechPath","Politics", "ProSports", "Other", "Journalism", "Architecture")
speed$race_o <-as.factor(speed$race_o) 
speed$dec_o <- as.factor(speed$dec_o)
speed$samerace <- as.factor(speed$samerace)

sd2 <- speed
sd2 <- sd2[ , -1] #IID  
sd2 <- sd2[, -1] #ID  
sd2 <- sd2[, -2] #IDG
sd2 <- sd2[, -3] #Wave
sd2 <- sd2[, -3] #Round
sd2 <- sd2[, -3] #Position
sd2 <- sd2[, -3] #Postion1
sd2 <- sd2[, -4] #Partner 
sd2 <- sd2[, -4] #PID
sd2 <- sd2[, -26]#Field
sd2 <- sd2[, -(27:29)]#Academics
sd2 <- sd2[,-(30:32)]#Socioeconomic 
sd2 <- sd2[,-33]#Career
sd2 <- sd2[,-(59:64)]#What others look for
sd2 <- sd2[,-(70:74)]#Others perception
sd2 <- sd2[,-(81:92)]#Data gathered after intitial
sd2 <- sd2[,(1:79)]
sd2 <- sd2[,-(70:79)] #Removes Post First Date
sd2 <- sd2[,-52]#exclude expnum

sdrandom <- sd2[sample(nrow(sd2), nrow(sd2)),] #Get a random sample since the data is organized by participant

sdclean <- na.omit(sdrandom) #Remove rows with NA values to create a "clean" set

train <- sdclean[1:5199, ]
test <- sdclean[5200:6499, ]
```

#Variable exploration
```{r}
explore <- sdclean
names(explore)

explore$gender <- factor(explore$gender, levels = c(0, 1), labels = c("Female", "Male"))


```

#Matching based on age

Age profile of people who participated in the events
```{r}
summary(explore$age)
ggplot(explore, aes(x=age , fill=gender))+ geom_histogram() + ggtitle("Age Distribution") + xlab("Participant Age Group")

```

Divide age of participants into <25, 25-30, 31-35, 36-40, 41-50, >50
```{r}
explore.age <- explore
explore.age$participant.age.group <- as.factor(ifelse(explore$age<25, "<25",
                                        ifelse(explore$age<31, "25-30", 
                                        ifelse(explore$age<36, "31-35",
                                        ifelse(explore$age<41, "36-40",
                                        ifelse(explore$age<51,"41-50",">50"))))))
#See the distribution of each age group
plot(explore.age$participant.age.group)
table(explore.age$participant.age.group)


#To calculate percentage of matching easier, convert "Yes" and "No" into numerical value 0,1
explore.age$match <- as.numeric(ifelse(explore$match == 1,1,0))

age.match.ratio <- explore.age %>% group_by(gender, participant.age.group) %>% summarise(match.prop = mean(match))

ggplot(age.match.ratio, aes(x = participant.age.group, y = match.prop, fill = gender)) + geom_col(position = "dodge")+ ylab("Matching Probability") + xlab("Participant Age Group")
```


Since there are only male in participant age group 41-50, there is only probability of matching for male sample. Interestingly, this group of male aged 41-50 has the highest probability to match. 1 in 4 of this sample group matched. In the most popular age group, the probability of male and female to match is really close, and male has slightly higher probability to match in group of age less than 25.

#Age correlation of participants and partners
```{r}
#Plot age of participant and age of partner 

age.match <- explore.age[c("age","age_o")]
ggplot(age.match, aes(x = age, y = age_o)) + geom_point()+ geom_smooth(method=lm) +ylab("Age of Partner")+ xlab("Age of Participant")+ggtitle("Age Match Plot")

#Age of participant and age of partner correlation

cor(age.match$age, age.match$age_o)
```

There is not much correlation between age of participants and age of partners.In fact, participants aged 55 matched with partners from age 20-40.
